---
title: "Maoist Conflict in India"
subtitle: "An Annotated Bibliography"
author: 
  - Emmanuel Teitelbaum, George Washington University
  - Shiva Sharma, George Washington University
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  pdf_document:
    citation_package: biblatex
biblatexoptions: [backend = biber, skipbib = true, labeldateparts = true, isbn = false, annotation = false, url = false, date = year]
biblio-style: chicago-authordate
bibliography: maoism.bib
geometry: margin = 1in
fontsize: 12pt
urlcolor: blue
header-includes: 
  - \usepackage[american]{babel}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, results="asis")
library(RefManageR)
bib <- ReadBib("maoism.bib", check=FALSE)
```


## Quantitative Studies on Maoism

\fullcite{Bohara2006}  
\begin{quote}
Abstract:
```{r Bohara2006}
cat(bib["Bohara2006"]$abstract)
```
\end{quote}

*Summary:*



\bigbreak

\fullcite{Dasgupta2017}
\begin{quote}
Abstract:
```{r Dasgupta2017}
cat(bib["Dasgupta2017"]$abstract)
```
\end{quote}

*Summary:*

This article exploits the unique roll-out of the NREGS program using a difference-in-difference
analysis to assess the impact of the MNREGA on Maoist violence. They also account for the local state
capacity using an index based on service delivery for the following: a paved road; ii) a primary school; iii)
a primary health center; iv) and an agricultural credit cooperative. The authors use the total number of
violent events and total fatalities as measures of conflict. They find that the roll-out of MNREGA causes a
large long-run reduction in Maoist violence. However, this is largely in districts “with sufficient pre-
existing local state capacity to implement the program effectively.” . The data for the analysis comprises
a district-level dataset using multiple local language press sources between 1999-2009.

\bigbreak

\fullcite{Gomes2015}
\begin{quote}
Abstract:
```{r Gomes2015}
cat(bib["Gomes2015"]$abstract)
```
\end{quote}

*Summary:*

To summarize the article, it says that... 

Questions: 

1) Is it true that the NSS data are representative at the district level? For Employment and Unemployment Survey, stratification at the district level only started with the in 2005-06(62nd round) onward. But perhaps it started earlier for the Household Consumer Expenditure Surveys; 

2) How is land inequality calculated for the analysis? Were the binned nature of the landholdings data taken into account?;

3) Are NSS data a good source for measures of inequality? My understanding was that they tended to under-represent the rich households. 

\bigbreak